\section{Discussion}

\subsection{Our conclusion}
From what we picked up from our research form, and from the research articles we found, latency plays a very important role in the wide-spread adoption of cloud gaming. Found from \textit{Figure 7, 8, 18, Section 3.2}, we have found that the higher the latency plays up with a cloud gaming service, that the performance quality can go down with a marked difference to little latency. Not only does increased latency cause performance to go down, but also the client's gaming experience, shown in \textit{Figure 9, 14, 15, 16, 17, Section 3.2}.
While most from the survey form claimed to have a strong internet connection with little or no latency issues, most had little or no interest in the concept of cloud gaming. Our hypothesis that we stated "Latency is the most important factor why people don't adopt cloud gaming" has seems to be proven wrong, because from the results of our survey, most of the respondents aren't interested right now in cloud gaming because they have a capable device to play their games on. But the respondents do think cloud gaming has a future, if they fix the other problems it has which latency is one of. We shouldn't ask "How do we remove latency?", instead, how do we manage it to make it tolerable for the client.
\subsection{What we can improve}
Many questions in our survey contained checkboxes where you could make more than one choice, most of the data became attributes with multiple values, which made it very difficult to visualize the data. Something else that was not very smart to include in our survey was the option to leave an open answer, which also led to difficult visualization. For the next survey we may create, we will leave out the open-answer option and make more use of closed questions or multiple-choice answers (one answer possible), to avoid attributes with multiple values and difficult visualisations.