\documentclass[]{report}
\renewcommand\thesection{\arabic{section}}%for page numbering in arabics
\usepackage{graphicx,tabularx}%for figures and tables
\usepackage[utf8]{inputenc} %allows special characters such as ä, ö, ỳ
\usepackage[english]{babel}  %set the language to English
\usepackage[margin=1.5in]{geometry} %change page margins 
\usepackage{sectsty}%section headers
\allsectionsfont{\sffamily\large}
\subsectionfont{\sffamily\normalsize}
\linespread{1.2}% line distance
\usepackage{lipsum}% http://ctan.org/pkg/lipsum
\usepackage{caption}%use for captions on tables
%use this exact command. The style and bibliographystyle has to be authoryear (Havard). The sorting is nyt: name, year, title so that the bibliography is sorted alphabetically. firstinits=true shortens the names: Albert Einstein -> A. Einstein
\usepackage[backend=bibtex,style=authoryear,bibstyle=authoryear,sorting=nyt,firstinits=true]{biblatex}
\setlength\parindent{0pt}%include this so that your paragraphs don't indent automatically
\addbibresource{library.bib} %this attaches your bib-file, your bibliography (must be in the same folder)
\usepackage[compact]{titlesec}%include title formatting package
\usepackage{float}

% Title Page
\title{What role does latency play in the wide-spread adoption of cloud gaming?}
\author{Jamie Meyer and Glenn Verstraelen}
\date{February 6th 2022 \\Module: SEAR \\Venlo, Limburg, Netherlands}


\begin{document}
\maketitle

\begin{abstract}
The purpose of this article is to show what our research is about and the research methods that have been used. Our results include a survey and found articles related to cloud gaming and latency. At first we have the introduction where we are going to talk about what cloud gaming is about, then we talk about latency and lastly we mention popular cloud gaming services. After the introduction, we will talk about our methods. In the methods section we talk about our survey and how we constructed it. After that, we will show the results from our survey and other sources regarding the topic. The discussion is our last section of the article, where we will answer our hypothesis. 
\pagenumbering{roman}
\end{abstract}

\tableofcontents
\setcounter{page}{3}
{%
	\let\oldnumberline\numberline%
	\renewcommand{\numberline}{\figurename~\oldnumberline}%
	\listoffigures%
}
%\listoftables %UNCOMMENT IF YOU HAVE TABLES
\pagebreak
\pagenumbering{arabic}	
	
\include{CloudGaming_Introduction} 
\include{CloudGaming_Methods} 
\include{CloudGaming_Result} 
\include{CloudGaming_Discussion} 

\printbibliography[title=References]



\appendix
\include{CloudGaming_Appendixes}

\end{document}
	
%\printbibliography[title=References]
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
	
  
