\documentclass[]{report}

\title{Survey cloud gaming}

\author{Jamie Meyer and Glenn Verstraelen}

\begin{document}
	\maketitle
	\pagebreak
	
	
	\begin{enumerate}
		\item What is your name?
		\item What is your gender?
		\item What is your age?
		\item How many hours did you spend on video games last week?
		\begin{enumerate}
			\item 0 hours
			\item 1 to 3 hours
			\item 4 to 6 hours
			\item 7 to 10 hours
			\item More than 10 hours
		\end{enumerate}
		\item Which operating system have you used to play video games in the last month?
		\begin{enumerate}
			\item Windows/Microsoft\item Mac/Apple
			\item Linux
			\item Other
		\end{enumerate}
		\item How much do you spend on video games (Monthly)?
		\begin{enumerate}
			\item €0 to €20
			\item €21 to €40
			\item €41 to €60
			\item €60+
		\end{enumerate}
		\item How important is the price on a Gaming Pc/laptop for you?
		\begin{enumerate}
			\item Super important
			\item Very important
			\item Important
			\item Somewhat important
			\item Not important
		\end{enumerate}
		\item How interested are you in cloud gaming?
		\begin{enumerate}
			\item Super interested
			\item Very interested
			\item Moderately interested
			\item Slightly interested
			\item Not interested
		\end{enumerate}
		\item Are you familiar with cloud gaming?
		\begin{enumerate}
			\item Super familiar
			\item Very familiar
			\item Moderately familiar
			\item Somewhat familiar
			\item Not familiar
		\end{enumerate}
		\item Based on your answers above, how likely are you to spend money on cloud gaming?
		\begin{enumerate}
			\item Super likely
			\item Very likely
			\item Somewhat likely
			\item Slightly
			\item Not really
		\end{enumerate}
		\item Do you think €10-€50 for cloud gaming is cheap, expensive, or reasonable?
		\begin{enumerate}
			\item Too cheap
			\item Somewhat cheap
			\item Reasonable
			\item Somewhat expensive
			\item Too expensive
		\end{enumerate}
		\item What services have you heard of that allows to game using cloud?
		\item What do you dislike most about gaming?
		\item Which of the following are reasons that you might join a subscription for cloud gaming?
		\item Do you think cloud gaming has a future in the video game industry?
		\begin{enumerate}
			\item Yes
			\item I am not sure
			\item No
		\end{enumerate}
		\item What kind of network connection do you use for gaming?
		\begin{enumerate}
			\item Wired connection
			\item Wireless connection (2.4 GHz)
			\item Wireless connection (5 GHz)
		\end{enumerate}
		\item What type of video games do you play the most?
		\begin{enumerate}
			\item Singleplayer
			\item Online Co-op
			\item Online multiplayer
			\item All of them
		\end{enumerate}
	\end{enumerate}

	
\end{document}